Code Clones: To refactor or not to refactor?

### 2020-05-09 ase/paper.tex
Updates from Overleaf

@@

% Experimental setup: how we validated that we fixed the problem
To simulate such refactorings in a controlled environment, we propose a tool that can automatically refactor a subset of duplication problems in Java source code. Our tool refactors 13k clones over 2k open-source Java projects and measures the delta maintainability scores of the refactoring.

@@

However, several studies show that not all clones should be refactored~\cite{jarzabek2010clones, kapser2008cloning}. This can be due to variance between cloned fragments~\cite{roy2007survey} or parts of the codebase that have a low coupling and evolve separately~\cite{jarzabek2010clones}. There are many tools to detect clones \cite{roy2007survey, sheneamer2016survey, svajlenko2014evaluating, gautam2016various} that can find similar pieces of code, but none show which clones are relevant refactoring candidates.

@@

In this study, we analyze the effect of clone refactoring on maintainability. We create a tool that automatically applies ``Extract Method'' refactorings to a subset of detected clones. We measure several maintainability metrics \cite{heitlager2007practical} before and after refactoring each clone to determine its impact on system maintainability. These metrics are volume, number of parameters, duplication and complexity. Using this setup, we gain empirical data about the maintainability improvement of clones on a large set of projects in a controlled environment. We use this data to define which characteristics of clones have the biggest influence on system maintainability when such a clone is refactored. This allows for more a accurate suggestion of code clones for refactoring and can assist in the refactoring process.

@@

Over a corpus of 2,267 Java project our tool refactored 12,710 clone classes. We found that the main influencing factor on maintainability when refactored is clone volume. %We define token volume as the combined number of tokens in all clone instances in a clone class. %When refactoring clones with a very small token volume, we found that the maintainability decreases when such clones are refactored. 
The average clone with a volume of 63 or more tokens improves maintainability when refactored. The other factor with a major influence on maintainability is the number of parameters that are required for the extracted method. We found that if a clone requires more than 2 parameters in the extracted method, it is more likely to decrease maintainability.

@@

\subsection{Clone harmfulness}

>>>>

\usepackage{todonotes}

@@

% Experimental setup: how we validated that we fixed the problem
To simulate such refactorings in a controlled environment, we create a tool that can automatically refactor a subset of duplication problems in Java source code. Our tool refactors 13k clones over 2k open-source Java projects and measures the delta maintainability scores of the refactoring.

@@

However, several studies show that not all clones should be refactored~\cite{jarzabek2010clones, kapser2008cloning}. This can be due to variance between cloned fragments~\cite{roy2007survey} or parts of the codebase that have a low coupling and evolve separately~\cite{jarzabek2010clones}. There are many tools to detect clones \cite{roy2007survey, sheneamer2016survey, svajlenko2014evaluating, gautam2016various} that can find similar pieces of code, but none show to which extent these are relevant refactoring candidates.

@@

In this study, we analyze the effect of clone refactoring on maintainability. We create a tool that automatically applies ``Extract Method'' refactorings to a subset of detected clones. We measure several maintainability metrics \cite{heitlager2007practical} before and after refactoring each clone to determine its impact on system maintainability. These metrics are volume, number of parameters, duplication and complexity. Using this setup, we gain empirical data about the maintainability improvement of clones on a large set of projects in a controlled environment. We use this data to understand which characteristics of clones have the biggest influence on system maintainability when refactoring. This allows for more a accurate suggestion of code clones for refactoring and can assist in the refactoring process.

@@

Over a corpus of 2,267 Java project our tool refactored 12,710 clone classes. We find that the main influencing factor on maintainability when refactored is clone volume. %We define token volume as the combined number of tokens in all clone instances in a clone class. %When refactoring clones with a very small token volume, we found that the maintainability decreases when such clones are refactored. 
The average clone with a volume of 63 or more tokens improves maintainability when refactored. The other factor with a major influence on maintainability is the number of parameters that are required for the extracted method. We find that if a clone requires more than 2 parameters in the extracted method, it is more likely to decrease maintainability.

@@

\subsection{Clone harmfulness}
\todo{incomplete}
